The new open source post processing method provides similar results for the stake positions as the software TBC.
Therefore the licensed TBC software can be replaced by the open source method.
\medskip

Based on the results of the measured and theoretically calculated ice velocities we can confirm the low velocities
measured in the last years.
With the applied measurement method, we were not able to measure accurate flow velocities of Blekumbreen and Tellbreen.
We can only specify upper limits for the velocity, which are
the uncertainties of 0.40 m for northing and 0.19 m for easting.
The theoretical surface velocity of the shallow ice approximation validates the small values for the horizontal velocity.
\medskip

Due to a faster movement in the vertical direction, it is possible to calculate
- even with an uncertainty of 0.89 m on the individual elevations -
a vertical velocity.
Thus we are able to calculate mass balances for both glaciers,
which shows that the whole area of the glaciers is in the ablation zone.
\medskip

With the findings in this report,
we are able to propose improvements to the setup and the methods,
which could eventually help to increase the accuracy of the collected coordinates and
enable the precise measurement of the very small flow velocities of the glaciers.\\
We found it helpful to measure some stakes two times.
If all stakes were measured two times,
a comparison of each two positions would offer a sound method of determining the uncertainties.\\
Even though we tried our best to correct the measurement data for the distance
of the rover to the stake and the inclination of some stakes,
the corrections did not reduce the uncertainties on the positions sufficiently.
Therefore, our suggestion for the improvement is make sure that stakes are always drilled straight.
We advise not to use inclined stakes at all for the velocity measurement,
because the error added by the high ablation values is hardly controllable.
Additionally, it would make the measuring procedure a lot simpler if the stake of the rover could be placed every time
into the stake, instead of next to it.
This could be achieved if the stakes are cut down to a reachable level every year when they have been melted out a lot.\\







